Verifying Spatial Properties of Array Computations

### 2017-04-14 oopsla17/oopsla17.tex
some editing in results

@@

\subsection{Study}
%
\noindent
We put together a corpus of around 1 million lines of Fortran code from a
\numPackages{} scientific computing packages ranging in size and scope: The Unified Model (UM)~\cite{um},
E3MG~\cite{RePEc:aen:journl:2006se-a12}, BLAS~\cite{blas},
Hybrid4~\cite{GBC:GBC635}, GEOS-Chem~\cite{geos-chem}, Navier (based
on \cite{griebel1997numerical}), Computational Physics
2~\cite{nicholas2006computational},
ARPACK-NG~\cite{arpackng}, and
SPECFEM3D~\cite{specfem3d}. Appendix~\ref{app:corpus} provides
further detail on these packages.

@@

\begin{itemize}
% (Vars, ...)
\item An assignment to a variable, with an RHS comprising some array
  computation, tends to correspond to a reduction (e.g., calculating
the max value in an array).

\end{itemize}

>>>>

\item Most loop-array computations of the previous form read
from arrays with a pattern that includes the immediate
neighbours (i.e., offset 1 from the induction variable);

@@

\subsection{Methodology}
%
\noindent
We constructed a corpus of around 1.4 million lines of Fortran code
(2.4 million including comments and white space) from a \numPackages{}
scientific computing packages ranging in size and scope: The Unified
Model (UM)~\cite{um}, E3MG~\cite{RePEc:aen:journl:2006se-a12},
BLAS~\cite{blas}, Hybrid4~\cite{GBC:GBC635},
GEOS-Chem~\cite{geos-chem}, Navier (based on
\cite{griebel1997numerical}), Computational Physics
2 (CP2) ~\cite{nicholas2006computational}, ARPACK-NG~\cite{arpackng}, and
SPECFEM3D~\cite{specfem3d}. \dnote{Include the rest}
Appendix~\ref{app:corpus} provides further detail on these packages.
Half of the packages come from research groups who 
are our project partners (\ie{}, they were
not selected carefully to skew results). BLAS was selected as it is
a common library in numerical code; similarly CP2 was selected as 
it presents a set of standard numerical analysis algorithms from a
popular computational physics textbook.

@@

\begin{itemize}
% (Vars, ...)
\item An assignment to a variable, with an RHS comprising some array
  computation, tends to correspond to a reduction (e.g., calculating
the max value in an array).
\end{itemize}

\subsection{Results}

\paragraph{Addressing the hypotheses}

\begin{enumerate}
\item Loops over arrays mainly read from arrays with a static pattern
based on constant offsets from (base or dervied) induction variables;
\end{enumerate}

%\begin{tabular}
%Neighbourhood or Constant Affine RHS &  Total 
%\end{tabular}
